---
title: '[Arturo de la Cruz Libardi](https://adlcruz.github.io/)'
description: A personal website
output: html_document
css: "relax.css" # "style.css"
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(rmarkdown);library(markdown);library(htmltools)
```

```{r}
htmltools::HTML("<hr>")
```

Work and study in the [*Environment and Health Modelling (EHM) Lab*](https://www.lshtm.ac.uk/research/centres-projects-groups/ehm-lab) at the [London School of Hygiene and Tropical Medicine](https://www.lshtm.ac.uk). I am focusing on the modelling of airborne pollutants for exposure assessment and epidemiological research.

[Work/Study profile](https://www.lshtm.ac.uk/aboutus/people/de-la-cruz-libardi.arturo)

[Publications/ORCID](https://orcid.org/0009-0001-1543-7999)

[github](https://github.com/AdlCruz "Code")

```{r}
htmltools::HTML("<hr>")
```

# R tools and packages

[**hipmapp**](https://ehm-lab.github.io/hipmapp/) **is a health impact projection mapping dashboard. [More on this](#hipmapp)**

[**rctapi**](https://adlcruz.github.io/rctapi/) **and [rctexplorer](https://adlcruz.github.io/rctexplorer/) are packages to interact with the [clinicaltrials.gov](https://www.clinicaltrials.gov/) online database. [More on these](#rctgovPacks).**

# Projects

###### hipmapp (2023) {#hipmapp}

[hipmapp](https://ehm-lab.github.io/hipmapp/) is a [climate impact projections tool](https://climate-adapt.eea.europa.eu/en/metadata/tools/exhaustion-health-impact-projections-tool) developed as a subdeliverable of [EXHAUSTION](https://climate-adapt.eea.europa.eu/en/metadata/publications/exhaustion-white-paper-exposure-to-heat-and-air-pollution-in-europe#:~:text=The%20EU%2Dfunded%20EXHAUSTION%20project,pollution%20and%20identify%20adaptation%20strategies) EU funded [project](https://cordis.europa.eu/project/id/820655). There was a [tweet](https://twitter.com/cinea_eu/status/1759871919476576732?ref_src=twsrc%5Etfw%7Ctwcamp%5Etweetembed%7Ctwterm%5E1759871919476576732%7Ctwgr%5E%7Ctwcon%5Es1_&ref_url=file%3A%2F%2F%2FC%3A%2FUsers%2FArturodelaCruz%2FOneDrive20-20London20School20of20Hygiene20and20Tropical20Medicine%2FAreas%2FRDrive%2Fpages_and_apps%2FAdlCruz.github.io%2Findex.html)

###### rctapi and rctexplorer (2021) {#rctgovPakcs}

[rctapi](https://adlcruz.github.io/rctapi/) + [rctexplorer](https://adlcruz.github.io/rctexplorer/) for R based interaction with the clinicaltrials.gov online database Use these two to search filter and download records from the website and load data to an app for interactive visualisation. Feel free to use/copy/improve on the [source code](https://github.com/AdlCruz/rctapi).

[Report and use-case.](assets/deanonlshtmdiss.pdf)\

Presented at the local R Users Group meeting [from 8:07]((https://lshtm.cloud.panopto.eu/Panopto/Pages/Viewer.aspx?id=2ae0141e-9685-4db2-a75f-af5400c191d0)), [pdf](linked_content/pres_RUGrctpkgs_2022/RUG_18Nov22_rct_presentation.pdf), [video demo](https://player.vimeo.com/video/595343322?h=97da0c4bb5).

###### Immediate and projected impact of Covid-19 on NHS cancer waiting time pathways (2021)

[Presentation](https://docs.google.com/presentation/d/1hhb2Vdc4sjZ0h_he6wof5eFAbhWj-NQB/edit#slide=id.p4)

[Report](assets/datachallengeReport.pdf)

The [MSc in Health Data Science](https://www.lshtm.ac.uk/study/courses/masters-degrees/health-data-science) at the London School of Hygiene and Tropical Medicine (2020-2021) was special. Not only were we the first cohort but we did it all without ever setting foot in the same building. The highlight of the year for me was the Data Challenge module which consisted of small teams taking on one large project each at the request of various stakeholders. I was lucky enough to team-up with some excellent individuals and together we worked on a pressing issue for the Royal College of Surgeons.

# Presented

-   ISEE Young, Rennes, June 2024, classic oral presentation: [slides](assets/adlcruz_ISEEYoung_Rennes_June2024.pdf)

-   Turing Climate Informatics, London, April 2024, poster presentation: [poster](assets/poster_turingcliminf_2024/poster_turingcliminf_adlcl.pdf)

# Courses

-   [Summer School 2023: “Processing and visualizing large geospatial data using R, Python and Julia”](https://opengeohub.org/summer-school/opengeohub-summer-school-poznan-2023/) 28 August - 1 September 2023

-   [Modern time series methods for public health and epidemiology (5 days course)](https://www.eepe.org/specialized-1-week-courses/) 8-12 July 2022

# Location

Madrid, Varese, London.

# Interests

-   My research areas
-   Neuroscience, Hiking, Sci-fi, Meadows, Orcas, Volleyball, Mountains, ...

# Unclassified

[The Role of Dopamine and Dopamine Receptor Signalling in Basal Ganglia-Mediated Action Selection](assets/lrpbsckcl.pdf).
