---
pagetitile: ""
title: ""
toc: false
lightbox: true
---
# Arturo de la Cruz Libardi

```{r echo=FALSE}
#| message: false
#| warning: false
#| paged-print: true
knitr::opts_chunk$set(echo=FALSE)
library(rmarkdown);library(markdown);library(htmltools)
```

```{r}
htmltools::HTML("<hr>")
```

>Work and study in the [*EHM Lab*](https://www.lshtm.ac.uk/research/centres-projects-groups/ehm-lab) at the [London School of Hygiene and Tropical Medicine](https://www.lshtm.ac.uk).  
>Focus: modelling airborne pollutants for exposure assessment and epidemiological research.

```{r}
htmltools::HTML("<hr>")
```

For more, this is my institutional [profile](https://www.lshtm.ac.uk/aboutus/people/de-la-cruz-libardi.arturo).  
My [ORCID](https://orcid.org/0009-0001-1543-7999) with publications and collaborations.  
And my [personal](https://github.com/AdlCruz) and [EHM-Lab GitHub](https://github.com/ehm-lab), where the code lives.  

```{r}
htmltools::HTML("<hr>")
```

### Other Interests

-   R, Neuroscience, Hiking, Sci-fi, Meadows, Interesting Words, Orcas, Volleyball, Mountains, ...

Feel free to reach out to me to chat about any of the above :)
