---
title: '[Arturo de la Cruz Libardi](https://adlcruz.github.io/)'
description: A personal website
output: html_document
css: "relax.css" # "style.css"
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(rmarkdown);library(markdown);library(htmltools)
```

```{r}
htmltools::HTML("<hr>")
```

Work and study in the [*EHM Lab*](https://www.lshtm.ac.uk/research/centres-projects-groups/ehm-lab) at the [London School of Hygiene and Tropical Medicine](https://www.lshtm.ac.uk).\
Focus: modelling airborne pollutants for exposure assessment and epidemiological research.

[Profile](https://www.lshtm.ac.uk/aboutus/people/de-la-cruz-libardi.arturo) \| [Publications](https://orcid.org/0009-0001-1543-7999) \| [GitHub](https://github.com/AdlCruz "Code")

```{r}
htmltools::HTML("<hr>")
```

### Projects

[**Mapping temperature-related mortality projections for 800+ European cities**](https://ehm-lab.github.io/hipmapp/) **(2023)**\
[App](https://ehm-lab.shinyapps.io/hipmapp/) \| [Description](https://climate-adapt.eea.europa.eu/en/metadata/tools/exhaustion-health-impact-projections-tool) \| [Parent](https://cordis.europa.eu/project/id/820655) \| [Tweet](https://twitter.com/cinea_eu/status/1759871919476576732?ref_src=twsrc%5Etfw%7Ctwcamp%5Etweetembed%7Ctwterm%5E1759871919476576732%7Ctwgr%5E%7Ctwcon%5Es1_&ref_url=file%3A%2F%2F%2FC%3A%2FUsers%2FArturodelaCruz%2FOneDrive20-20London20School20of20Hygiene20and20Tropical20Medicine%2FAreas%2FRDrive%2Fpages_and_apps%2FAdlCruz.github.io%2Findex.html)

[**Enabling search, filter, download (rctapi),**](https://adlcruz.github.io/rctapi/) [**and interactive exploration (rctexplorer) including of potential treatment networks from**](https://adlcruz.github.io/rctexplorer/) [**a (very) large clinical trial registry** ](https://clinicaltrials.gov/) **(2021)**\
[Report and use-case](assets/deanonlshtmdiss.pdf) \| [RUG presentation (from 8:076)](https://lshtm.cloud.panopto.eu/Panopto/Pages/Viewer.aspx?id=2ae0141e-9685-4db2-a75f-af5400c191d0) [(pdf)](linked_content/pres_RUGrctpkgs_2022/RUG_18Nov22_rct_presentation.pdf)

[**Immediate and projected impact of Covid-19 on NHS cancer waiting time pathways**](page_datachallenge.html) **(2021)**  
[Report](assets/datachallengeReport.pdf) | [Presentation](https://docs.google.com/presentation/d/1hhb2Vdc4sjZ0h_he6wof5eFAbhWj-NQB/edit#slide=id.p4)

### Presented

-   ISEE Young, Rennes, June 2024, classic oral presentation: [slides](assets/adlcruz_ISEEYoung_Rennes_June2024.pdf)\
-   Turing Climate Informatics, London, April 2024, poster presentation: [poster](assets/poster_turingcliminf_2024/poster_turingcliminf_adlcl.pdf)

### Courses attended

-   [Summer School 2023: “Processing and visualizing large geospatial data using R, Python and Julia”](https://opengeohub.org/summer-school/opengeohub-summer-school-poznan-2023/) 28 August - 1 September 2023\
-   [Modern time series methods for public health and epidemiology (5 days course)](https://www.eepe.org/specialized-1-week-courses/) 8-12 July 2022

### Location

London, Varese, Madrid.

### Interests

-   My research areas
-   R, Neuroscience, Hiking, Sci-fi, Meadows, Orcas, Volleyball, Mountains, ...

### Other linked content

[Big data in environmental epidemiology lecture slides](linked_content/pres_bigdataenvepi_2024/bdee_slides.html).\
[The Role of Dopamine and Dopamine Receptor Signalling in Basal Ganglia-Mediated Action Selection](assets/lrpbsckcl.pdf).

### this is the end of the page

for your persistence you are rewarded with the option to spend as much time as you want reading a few of the book reviews, stories, and other odd things I have written in the past 20 or so years in this humbly named [blog](https://cruzadl.github.io/), don't waste your time :)
