---
title: https://adlcruz.github.io/ 
description: A personal website
output: html_document
css: "relax.css" # "style.css"
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(rmarkdown);library(markdown);library(htmltools)
```

```{r}
htmltools::HTML("<br>")
```

Work and study on improving the availability and quality of air pollution data for epidemiological analyses with statistical learning methods at the [London School of Hygiene and Tropical Medicine](www.lshtm.ac.uk) and [*Environment and Health Modelling (EHM) Lab*](https://www.lshtm.ac.uk/research/centres-projects-groups/ehm-lab).

```{r}
htmltools::HTML("<hr>")
```

[https://www.lshtm.ac.uk/aboutus/people/de-la-cruz-libardi.arturo](https://www.lshtm.ac.uk/aboutus/people/de-la-cruz-libardi.arturo)

[https://orcid.org/0009-0001-1543-7999](https://orcid.org/0009-0001-1543-7999)

[github AdlCruz](https://github.com/AdlCruz)\

[\@dlCruzArturo](https://twitter.com/dlCruzArturo)\

```{r}
htmltools::HTML("<hr>")
```

# R packages

**[hipmapp](https://ehm-lab.github.io/hipmapp/) is a health impact projection mapping dashboard** developed within the broader [EXHAUSTION](https://climate-adapt.eea.europa.eu/en/metadata/publications/exhaustion-white-paper-exposure-to-heat-and-air-pollution-in-europe#:~:text=The%20EU%2Dfunded%20EXHAUSTION%20project,pollution%20and%20identify%20adaptation%20strategies) EU funded [project](https://cordis.europa.eu/project/id/820655), and omg it got tweeted as well wow look at that

<blockquote class="twitter-tweet"><p lang="en" dir="ltr"><a href="https://twitter.com/hashtag/ProjectHighlight?src=hash&amp;ref_src=twsrc%5Etfw">#ProjectHighlight</a><a href="https://twitter.com/ExhaustionH2020?ref_src=twsrc%5Etfw">@ExhaustionH2020</a> project has come to an end. <br>Check their interactive tool on how climate change will affect human lives in urban settings 👉 <a href="https://t.co/czUSmjnfts">https://t.co/czUSmjnfts</a><a href="https://twitter.com/hashtag/H2020?src=hash&amp;ref_src=twsrc%5Etfw">#H2020</a> <a href="https://twitter.com/hashtag/Climate?src=hash&amp;ref_src=twsrc%5Etfw">#Climate</a> <a href="https://twitter.com/hashtag/EU?src=hash&amp;ref_src=twsrc%5Etfw">#EU</a> <a href="https://twitter.com/hashtag/Research?src=hash&amp;ref_src=twsrc%5Etfw">#Research</a> <a href="https://twitter.com/hashtag/ResearchImpactEU?src=hash&amp;ref_src=twsrc%5Etfw">#ResearchImpactEU</a> <a href="https://t.co/GECEyd86kl">pic.twitter.com/GECEyd86kl</a></p>&mdash; CINEA🇪🇺 (@cinea_eu) <a href="https://twitter.com/cinea_eu/status/1759871919476576732?ref_src=twsrc%5Etfw">February 20, 2024</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

_moving on_

**[rctapi](https://adlcruz.github.io/rctapi/) + [rctexplorer](https://adlcruz.github.io/rctexplorer/) for R based interaction with the clinicaltrials.gov online database**
Use these two to search filter and download records from the website and load data to an app for interactive visualisation. Feel free to use/copy/improve on the [source code](https://github.com/AdlCruz/rctapi).

[Project report and use-case](assets/deanonlshtmdiss.pdf) \

Presented at the local R Users Group meeting [from 8:07]((https://lshtm.cloud.panopto.eu/Panopto/Pages/Viewer.aspx?id=2ae0141e-9685-4db2-a75f-af5400c191d0)), [pdf](linked_content/pres_RUGrctpkgs_2022/RUG_18Nov22_rct_presentation.pdf), [video demo](https://player.vimeo.com/video/595343322?h=97da0c4bb5).

# Presented

  - Turing Climate Informatics <a href="assets/poster_turingcliminf_2024/poster_turingcliminf_adlcl.pdf" target="_blank"> poster </a> and <a href="assets/poster_turingcliminf_2024/poster_turingcliminf_refs_adlcl.pdf" target="_blank"> references </a> - 23-04-2024
  
  - DASH Centre Launch <a href="assets/poster_dashlaunch_2024/poster_dashlaunch_adlcl.pdf" target="_blank"> poster </a> and <a href="assets/poster_dashlaunch_2024/poster_dashlaunch_refs_adlcl.pdf" target="_blank"> references </a> - 26-03-2024

  - environmental epidemiology module 
  <a href="linked_content/pres_bigdataenvepi_2024/bdee_slides.html" target="_blank">lecture slides</a>  big data in environmental epidemiology - 14-03-2024
  
  - LSHTM R Users Group  <a href="linked_content/pres_RUGrctpkgs_2022/RUG_18Nov22_rct_presentation.pdf" target="_blank"> R packages presentation </a> - 18-11-2022
  
# Location

Madrid, Varese, London.

# Interest

-   Predictive modelling, Exposure assessment, Epidemiology
-   Neuroscience, Hiking, Sci-fi, Meadows, Orcas, Volleyball, Mountains, ...

# Unclassified

[The Role of Dopamine and Dopamine Receptor Signalling in Basal Ganglia-Mediated Action Selection](assets/lrpbsckcl.pdf).

