---
title: Arturo de la Cruz Libardi
description: Zoom right down
output: 
  html_document: 
    css: "frontpage.css"
---


```{r echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(rmarkdown);library(markdown);library(htmltools)
```

```{r}
htmltools::HTML("<hr>")
```

*Research Assistant in Health Data Science,*   
[*Environment and Health Modelling (EHM) Lab,*](https://www.lshtm.ac.uk/research/centres-projects-groups/ehm-lab)  
*Department of Public Health, Environments and Society,*  
[*London School of Hygiene and Tropical Medicine*](https://www.lshtm.ac.uk/)

### Profile and work

[Here (profile)](https://www.lshtm.ac.uk/aboutus/people/de-la-cruz-libardi.arturo) and [here work (DOIs)](https://orcid.org/0009-0001-1543-7999)

### Contact

[Arturo.de-la-Cruz-Libardi\@lshtm.ac.uk](mailto:Arturo.de-la-Cruz-Libardi@lshtm.ac.uk)\
[github AdlCruz](https://github.com/AdlCruz)\
[\@dlCruzArturo](https://twitter.com/dlCruzArturo)\

### ["Local" Links Link](linked_content.html)

```{r}
htmltools::HTML("<hr>")
```

### R packages

> **rctapi + rctexplorer: R based interaction with clinicaltrials.gov online database**\
> [rctapi](https://adlcruz.github.io/rctapi/) - search filter and download records\
> [rctexplorer](https://adlcruz.github.io/rctexplorer/) - load data to R shiny app for interactive visualisation\

> *Comprehensive project report and use-case example*\
> [Building and testing R tools to extract and explore data from the online database ClinicalTrials.gov](assets/deanonlshtmdiss.pdf)\

Rctapi and rctexplorer at the local R Users Group meeting [from 8:07]((https://lshtm.cloud.panopto.eu/Panopto/Pages/Viewer.aspx?id=2ae0141e-9685-4db2-a75f-af5400c191d0)), just the slides as [dynamic carousel](linked_content/pres_RUGrctpkgs_2022/rct_presentation.html) or [static pdf](linked_content/pres_RUGrctpkgs_2022/RUG_18Nov22_rct_presentation.pdf).

[Video demonstration on Vimeo](https://player.vimeo.com/video/595343322?h=97da0c4bb5).

```{r}
htmltools::HTML("<hr>")
```

### Neuroscience literature review (BSc fulfilment)

> [The Role of Dopamine and Dopamine Receptor Signalling in Basal Ganglia-Mediated Action Selection](assets/lrpbsckcl.pdf)

```{r}
htmltools::HTML("<hr>")
```

### Interests

-   Environmental Modelling, Epidemiology
-   R, Open Science, Free Software Principles, Science Fiction, Rational Optimism, Hiking, Meadows, Orcas, Volleyball, Mountains, ...
